Parallel Adaptive Importance Sampling

### 2016-06-02 PAIS.tex
Sections summary updated

***SECTIONS SUMMARY NEEDS REWRITING***

>>>>

In Section \ref{Sec:Prelim} we introduce some mathematical
preliminaries upon which we will later rely. In Section \ref{Sec:PAIS}
we present the general framework of the PAIS algorithm. In Section
\ref{Sec:adapt} we consider adaptive versions of PAIS which
automatically tune algorithmic parameters concerned with the proposal
distributions. In Section \ref{sec:AMR} we introduce the approximate
multinomial resampling (AMR) algorithm which is a less accurate but
faster alternative to the ETPF resampler. In Section \ref{Sec:Num} we
present some numerical examples, before a brief conclusion and
discussion in Section \ref{Sec:Conc}.
